Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
proofreading. minor edits

The contributions for the velocity term in equation (\ref{eq:Pinp_kin}), which should be the relative velocity between the planet and the solar wind, are given by the stellar wind velocity, the planetary orbital velocity, and the infall velocity (i.e., the velocity due to falling in the planet's gravitional field).
While $v_{\rm sw}$ is $\sim$30~km/s, the orbital velocity is $10-30~{\rm km/s}$ depending on the orbital distance (ranging from $1-5~{\rm AU}$), and the infall velocity from the planetary gravity is $\sim 10-25~{\rm km/s}$, depending on the planetary mass (ranging from $1 M_{\rm J}-10 M_{\rm J}$). Here, we simply consider
%%%%%%%%%% 
\begin{equation}
\frac{v}{v_{\odot}} \sim 10^{-1} \, . \label{eq:scale_v}
\end{equation}
%%%%%%%%%%
as a fiducial value for normalization.

@@

\paragraph{Modulation due to planetary spin rotation (a few hours $\sim $)}
The probability of the occurrence of the Jovian radio burst is correlated with the spin rotation phase \citep{dessler1983} due to the misalignment between the magnetic axis and the spin axis. If the time resolution of the observations is high enough, we might detect the periodicity due to planetary spin rotation. 
%
\paragraph{Modulation due to the presence of satellites (a few days $\sim $)}
The occurrence probability of Jovian radio burst is affected by the location of Io as well \citep{dessler1983}, because Io disturbs the surrounding electromagnetic field. 
Likewise, if the exoplanets have moons that emit plasmas, then the radio flux is  modulated by the orbital motion of the moon \citep[see e.g.,][]{noyola2014}.

@@

%
\paragraph{Modulation due to orbital motion of the planet (a few years $\sim $)}
If the planetary orbit is close to the edge-on configuration, the radio emission disappears concurrently with the planetary orbital motion, due to the increased plasma cut-off frequency along the path and/or secondary eclipse.
The former is because when the planet is behind the star the path of the radio emission toward the Earth comes through the vicinity of the star where the plasma density is high.
The probability of the latter one, secondary eclipse, is $\sim R_\star/a \sim 9$\% (in the case that $R_{\star}=100R_{\odot }$ and $a=5~\mathrm{AU}$). 
%

@@

Once radio emission is detected, it provides some useful information through both time dependence and frequency dependence. 
As mentioned in \S\ref{ss:timevariability}, auroral radio flux significantly varies in time in association with several physical processes. In turn, we could utilize the time variability to characterize the system. For example, if the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could be detectable. 
Long term monitoring could reveal the time variability corresponding to orbital period if the system is near edge-on. Modulation on timescale of a few days may imply the presence of satellites.

@@

A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind. Due to the great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars. 
The most promising targets are massive planetary ($M_p \gtrsim 4 M_{\rm J}$ companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).

>>>>

The contributions for the velocity term in equation (\ref{eq:Pinp_kin}), which should be the relative velocity between the planet and the solar wind, are given by the stellar wind velocity, the planetary orbital velocity, and the infall velocity (i.e., the velocity due to falling in the planet's gravitional field).
While $v_{\rm sw}$ is $\sim$30~km/s, the orbital velocity is $10-30~{\rm km/s}$ depending on the orbital distance (ranging from $1-5~{\rm AU}$), and the infall velocity from the planetary gravity is $\sim 10-25~{\rm km/s}$, depending on the planetary mass (ranging from $1 M_{\rm J}-10 M_{\rm J}$). 
In the next section, we simply consider
%%%%%%%%%% 
\begin{equation}
\frac{v}{v_{\odot}} \sim 10^{-1} \, . \label{eq:scale_v}
\end{equation}
%%%%%%%%%%
as a fiducial value for normalization.

@@

\paragraph{Modulation due to planetary spin rotation (a few hours $\sim $)}
The probability of the occurrence of the Jovian radio burst is correlated with the spin rotation phase \citep[e.g.][]{dessler1983} due to the misalignment between the magnetic axis and the spin axis. If the time resolution of the observations is high enough, we might detect the periodicity due to planetary spin rotation. 
%
\paragraph{Modulation due to the presence of satellites (a few days $\sim $)}
The occurrence probability of Jovian radio burst is affected by the location of Io as well \citep{dessler1983}, because Io disturbs the surrounding electromagnetic field. 
Likewise, if the exoplanets have moons that emit plasmas, then the radio flux is  modulated by the orbital motion of the moon \citep[see e.g.,][]{noyola2014}.

@@

%
\paragraph{Modulation due to orbital motion of the planet (a few years $\sim $)}
If the planetary orbit is close to the edge-on configuration, the radio emission disappears concurrently with the planetary orbital motion, due to the increased plasma cut-off frequency along the path and/or secondary eclipse \citep{lecavelier_et_al2013}. 
The former is because when the planet is behind the star the path of the radio emission toward the Earth comes through the vicinity of the star where the plasma density is high.
The probability of the latter one, secondary eclipse, is $\sim R_\star/a \sim 9$\% (in the case that $R_{\star}=100R_{\odot }$ and $a=5~\mathrm{AU}$). 
%

@@

Once radio emission is detected, it provides some useful information about the planet itself and the stellar wind through the time dependence and frequency dependence. 
As mentioned in \S\ref{ss:timevariability}, auroral radio flux significantly varies in time in association with several physical processes. In turn, we could utilize the time variability to characterize the system. For example, if the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could be detectable. 
Long term monitoring could reveal the time variability corresponding to orbital period if the system is near edge-on. Modulation on timescale of a few days may imply the presence of satellites.

@@

A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind. Due to the great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars, making planetary-mass companions to AGB stars unpromising for the search of planetary auroral radio emission. 
The most promising targets are massive planetary companions ($M_p \gtrsim 4 M_{\rm J}$ to red giant stars, with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
